The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-08 src/paper/results/robustness_to_sensitivity_assumptions.tex
Fix problems with references.

Our result that frequent and large scale rapid testing was responsible for a
large decrease in cases in the spring of 2021 in Germany seems to be at odds
with the general perception that rapid tests are unreliable. They also seem to
contradict recent studies showing that the actual sensitivity of rapid tests
might be lower than advertised (e.g.\cite{Scheiblauer2021}).

@@

% what is available -> two step mapping
Unfortunately, such sensitivity profiles are not usually reported in studies. We
thus need to create them by combining two types of studies: 1. Studies that
report the viral load in terms of threshold cycle ($C_t$) values determined by
PCR test 
(e.g. \cite{Cosentino2022}
, \cite{Ong2021}, 
\cite{Bonnet2022},
\cite{Jang2021} and \cite{Zuin2021}
). 2. Studies that report the ensitivity of
rapid tests for different $C_t$ values 
(e.g. \cite{Scheiblauer2021},
\cite{Bruemmer2021}).

@@

% Describe sensitivity lookupd vs. interpolation
For the mapping of $C_t$ values to rapid test sensitivities, again we have two
options. First, we can simply look up the discretized values for the three $C_t$
bins provided in \cite{Scheiblauer2021} (below 20, 25 to 30 and above 35).
Secondly, we can use linear regression to estimate a continous mapping for the
relationship by assuming that the $C_t$ values of each bin are achieved exactly
at the bin midpoints and that the relationship is linear.

>>>>

Our result that frequent and large scale rapid testing was responsible for a
large decrease in cases in the spring of 2021 in Germany seems to be at odds
with the general perception that rapid tests are unreliable. They also seem to
contradict recent studies showing that the actual sensitivity of rapid tests t
be lower than advertised (e.g.\cite{Scheiblauer2021}).

@@

% what is available -> two step mapping
Unfortunately, such sensitivity profiles are not usually reported in studies. We
thus need to create them by combining two types of studies: 1. Studies that
report the viral load in terms of threshold cycle ($C_t$) values determined by
PCR test (e.g. \cite{Cosentino2022}, \cite{Ong2021}, \cite{Bonnet2022},
\cite{Jang2021} and \cite{Zuin2021}). 2. Studies that report the ensitivity of
rapid tests for different $C_t$ values (e.g. \cite{Scheiblauer2021},
\cite{Bruemmer2021}).

@@

% Describe sensitivity lookupd vs. interpolation
For the mapping of $C_t$ values to rapid test sensitivities, again we have two
options. First, we can simply look up the discretized values for the three $C_t$
provided in \cite{Scheiblauer2021} (below 20, 25 to 30 and above 35). Secondly,
we can use linear regression to estimate a continous mapping for the
relationship by assuming that the $C_t$ values of each bin are achieved exactly
at the bin midpoints and that the relationship is linear.
